Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-18 manuscript.Rmd
More cleanup on the repo.

```{r LoadDatabase}
rm(list=ls())
load("HistoricalDatabase.R")

head(full.df)
dim(full.df)
```

```{r colorThemes}
# http://colorbrewer2.org/?type=diverging&scheme=PuOr&n=4

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
```

```{r summarySetUp, eval=FALSE, cache=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r Figure 1a - Journals, cache=TRUE, eval=FALSE}
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

#=======================================
# Journals
#=======================================
library(gridExtra)

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

@@

# Read Scopus database
scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHarvest.csv")

@@

 abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

@@

```{r plot03_AuthorPages, eval=FALSE, cache=FALSE}

@@

setwd("/Users/beperron/Git/SocialWorkResearch/Data")
sangam <- read.csv("sangam.csv")

>>>>

```{r Initialization}
rm(list=ls())
library(dplyr)
library(ggplot2)
library(gridExtra)
source("./Functions/pretty.R")

# Load data files
load("./Data/HistoricalDatabase.RData")
hodge.df <- readLines("./Data/hodge.txt", n = -1)
scopus.df <- read.csv("./Data/scopus.csv")
abb.df <- read.csv("./Data/master.csv")
sangam.df <- read.csv("./Data/sangam.csv")

# Create colour palette for consistent plotting
# http://colorbrewer2.org/?type=diverging&scheme=PuOr&n=4
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
```

```{r summarySetUp, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
  group_by(record) %>%
  summarise(N = n())

@@

```{r Figure 1a - Journals, eval=FALSE}

#=======================================
# Journals
#=======================================

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + geom_line()

    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

@@

# Read Scopus database
#scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHar#vest.csv")

@@

 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

@@

```{r plot03_AuthorPages, eval=FALSE}

@@
